%
% main.tex
%
% Copyright The TTC 2.0 Contributors.
%
% TTC 2.0 Documentation
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 4.0
% International License. To view a copy of this license,
% visit http://creativecommons.org/licenses/by-sa/4.0/.
%

%
% \brief Main file.
%
% \author Gabriel Mariano Marcelino <gabriel.mm8@gmail.com>
%
% \version 0.3.0
%
% \date 2021/04/01
%


\documentclass[a4paper,12pt]{book}

\usepackage{spacelab_book}

\title{TTC 2.0 Documentation}
\author{SpaceLab}
\date{\today}

% File metadata
\hypersetup
{
    pdfauthor   = {SpaceLab},
    pdfsubject  = {\thetitle},
    pdftitle    = {\thetitle},
    pdfkeywords = {Nanosatellites, CubeSats, TTC}
}

\begin{document}

    \pagenumbering{roman}
    \setcounter{page}{1}

    \input{header/titlepage}
    \cleardoublepage
    \input{header/authorpage}
    \cleardoublepage

    \listoffigures
    \addcontentsline{toc}{chapter}{List of Figures}

    \listoftables
    \addcontentsline{toc}{chapter}{List of Tables}

%----------- Nomenclature List ---------------
\nomenclature{\textbf{PCB}}{\textit{Printed Circuit Board.}}
\nomenclature{\textbf{GOLDS}}{\textit{Global Open coLlecting Data System.}}
\nomenclature{\textbf{UFSC}}{\textit{Universidade Federal de Santa Catarina.}}
\nomenclature{\textbf{RAM}}{\textit{Random Access Memory.}}
\nomenclature{\textbf{RF}}{\textit{Radio Frequency.}}
\nomenclature{\textbf{SRAM}}{\textit{Static Random Access Memory.}}
\nomenclature{\textbf{GFSK}}{\textit{Gaussian Frequency Shift Keying.}}
\nomenclature{\textbf{GMSK}}{\textit{Gaussian Minimum Shift Keying.}}
\nomenclature{\textbf{NGHam}}{\textit{Next Generation Ham Radio.}}\nomenclature{\textbf{UART}}{\textit{Universal Asynchronous Receiver / Transmitter.}}
\nomenclature{\textbf{SPI}}{\textit{Serial Peripheral Interface.}}
\nomenclature{\textbf{HAL}}{\textit{Hardware Abstraction Layer.}}
\nomenclature{\textbf{I$^2$C}}{\textit{Inter-Integrated Circuit.}}
\nomenclature{\textbf{RTOS}}{\textit{Real Time Operating System.}}
\nomenclature{\textbf{OBDH}}{\textit{On-Board Data Handling.}}
\nomenclature{\textbf{EPS}}{\textit{Electric Power System.}}
\nomenclature{\textbf{uC}}{\textit{MicroController.}}
\nomenclature{\textbf{FEC}}{\textit{Forward Error Correction.}}
\nomenclature{\textbf{RS}}{\textit{Reed-Solomon.}}
\nomenclature{\textbf{JTAG}}{\textit{Joint Test Action Group.}}
\nomenclature{\textbf{SDR}}{\textit{Software-Defined Radio.}}
\nomenclature{\textbf{EM}}{\textit{Engineering Model.}}
\nomenclature{\textbf{FM}}{\textit{Flight Model.}}
\nomenclature{\textbf{TTC}}{\textit{Telemetry, Tracking and Command.}}
%-----------------------------------------

    \printnomenclature
    \addcontentsline{toc}{chapter}{Nomenclature}

    \tableofcontents
    \cleardoublepage
    
    \pagenumbering{arabic}
    \setcounter{page}{1}

    \input{chapters/introduction}
    \input{chapters/hardware}
    \input{chapters/firmware}
    \input{chapters/operation}
    \input{chapters/assembly}
    \input{chapters/references}
    \input{appendices/appendices}

\end{document}